Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-08 Latex/journal_v1/V5/pr.tex
add code

Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
\end{split}
\end{equation}
Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
      0 & \text{otherwise}
    \end{cases}
\end{equation}
Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{lemma}
Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
The complexity order of this problem is about $O(\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

As we mentioned before, the complexity order of the first sub-problem is about $O(N_u \times K)$

@@

So the complexity of the main problem \eqref{problem} is $O(\mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.

@@

Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances. mMTC service includes a large number of UEs with low data rates and low power. 
Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to the end-to-end delay. The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
\begin{figure}
  %\centering 
    \includegraphics[scale = 0.4]{mmTCpower.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC services vs. Number of UE in each Service for three different mMTC service instances}
  \label{fig:8}
\end{figure}

>>>>

Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
\end{split}
\end{equation}
Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
      0 & \text{otherwise}
    \end{cases}
\end{equation}
Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{lemma}
Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

Also, assume that the algorithm converges after $T_{conv}$ times.
As we mentioned before, the complexity order of the first sub-problem is about $O(T_{conv} \times \mathfrak{N} \times K)$

@@

So the complexity of the main problem \eqref{problem} is $O(T_{conv} \times \mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.

@@

Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances. mMTC service includes a large number of UEs with low data rates and low power. 
Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to the end-to-end delay. Also, suppose the fronthaul link has no restrictions  .The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
\begin{figure}
  %\centering 
    \includegraphics[scale = 0.4]{mmTCpower.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC services vs. Number of UE in each Service for three different mMTC service instances}
  \label{fig:8}
\end{figure}
